Whole-body connectome of a segmented annelid larva

### 2024-06-16 README.Rmd
add Zenodo link to repo
README and Citation: update

@@

> Gáspár Jékely, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi (2024)
 \. _`r Title`_. Name of journal/book <>

@@

> Gáspár Jékely, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi (2024). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Gáspár Jékely, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: text](/Manuscript.qmd): Quarto source document
    for manuscript. Includes text, references and inserts the latest version of the figures from the /Figures folder. 
There is also a rendered html version,
    `Manuscript.html`, suitable for reading.

  - [:file\_folder: data](/data): Data used in the analysis.
  - [:file\_folder: scripts](/code): scripts used in the analysis.
  - [:file\_folder: figures](/pictures): Plots and other
    illustrations
  - [:file\_folder:
    supplements](/supplements):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
  - [:file\_folder:
    source_data](/source_data):
    Source data files associated with each figure containing all data points that have been plotted in the figure.

>>>>

[![DOI](https://zenodo.org/badge/773035678.svg)](https://zenodo.org/doi/10.5281/zenodo.10825370)

@@

> Csaba Verasztó, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, Gáspár Jékely (2024)
 \. _`r Title`_. Name of journal/book <>

@@

> Csaba Verasztó, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, Gáspár Jékely (2024). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Csaba Verasztó, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, , Gáspár Jékely, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://zenodo.org/doi/10.5281/zenodo.10825370>

@@

  - [:file\_folder: text](Manuscript.qmd): Quarto source document
    for manuscript. Includes text, references and inserts the latest version of the figures from the /Figures folder. 
There is also a rendered html version,
    `Manuscript.html`, suitable for reading.

  - [:file\_folder: data](/data): Data used in the analysis.
  - [:file\_folder: scripts](/code): scripts used in the analysis.
  - [:file\_folder: images](/pictures): Plots and other
    illustrations  
  - [:file\_folder: figures](/Figures): All figures for the paper
  - [:file\_folder: supplements](/supplements):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
  - [:file\_folder: source_data](/source_data):
    Source data files associated with each figure containing all data points that have been plotted in the figure.
